<header style="text-align: center">

### 2019-05-22 report/report.Rmd
Add grouped time series plots for nearby airports

- Find # of flights in nearby airports vs. time (group time series)

>>>>

```{r, fig.align='center', fig.height=2.5}
ddr.times(data$real$flights, 'EBCI', event, group = 'nearby')
# ddr.times(data$real$flights, 'EBLF', event, group = 'nearby')
ddr.times(data$real$flights, 'EHEH', event, group = 'nearby')
ddr.times(data$real$flights, 'EBAW', event, group = 'nearby')
ddr.times(data$real$flights, 'LFQQ', event, group = 'nearby')
```
